Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-04-16 manuscript.qmd
colorize contra table

```{python}
#| echo: false
#| label: tbl-contra
#| tbl-cap: Contralateral involvement depending on whether the primary tumor extends over the mid-sagittal line, the T-category, and whether the ipsilateral LNL III was involved or healthy.
def right_align(column) -> str:
  """Right align some columns."""
  return ["text-align: right"] * len(column)

@@

involved = num_involved.join(
  100 * percent_involved,
  rsuffix=" (%)",
).sort_index(axis="columns")
involved.columns = pd.MultiIndex.from_product(
  [["I", "II", "III", "IV"],
   ["n", "%"]],
  names=["LNL", ""]
)
(
  involved
  .reset_index()
  .style
  .format(precision=2)
  .apply(right_align, axis="index")
  .hide()
)
```

>>>>

```{python}
#| echo: false
#| label: tbl-contra
#| tbl-cap: Contralateral involvement depending on whether the primary tumor extends over the mid-sagittal line, the T-category, and whether the ipsilateral LNL III was involved or healthy.
def right_align(column: pd.Series) -> list[str]:
  """Right align some columns."""
  return ["text-align: right"] * len(column)

def highlight_bool(
  column: pd.Series,
  c_false: str = COLORS["green"],
  c_true: str = COLORS["red"],
) -> list[str]:
  """Make cell read (`False`) or green (`True`)."""
  n = len(column)
  trues = pd.Series([c_true] * n)
  falses = pd.Series([c_false] * n)
  colors = trues.where(column, falses)
  return colors.map(lambda x: f"color: {x}")

def highlight_t_stage(
  column: pd.Series,
  c_early: str = COLORS["green"],
  c_late: str = COLORS["red"],
) -> list[str]:
  """Highlight `early` and `late`."""
  is_early = column == "early"
  return highlight_bool(is_early, c_false=c_late, c_true=c_early)

@@

involved = num_involved.join(
  100 * percent_involved,
  rsuffix=" (%)",
).sort_index(axis="columns")
involved.columns = pd.MultiIndex.from_product(
  [["I", "II", "III", "IV"],
   ["n", "%"]],
  names=["LNL", ""]
)
(
  involved
  .reset_index()
  .style
  .format(precision=2)
  .apply(right_align, subset=involved.columns[0:])
  .apply(highlight_bool, subset=["Mid. ext.", "ipsi III"])
  .apply(highlight_t_stage, subset=["T-cat."])
  .hide()
)
```
